Sensor Clusterization in D-optimal Design in Infinite Dimensional Bayesian Linear Inverse Problems

### 2023-01-08 latex/paper.tex
Refined proposition statement on eigenvalues, present optimality as a corollary

  Let $\obs$ an observation operator such that $\obs^*\obs$ has the
  same eigenvectors as $\fwd \prcov \fwd^*$. If $\eta_i > 0$ for
  $i\leq k$ and $\obs^*\obs$ has eigenvalues $\eta_i$, then $\obs$
  maximizes $\tar$ subject to $\sum_{i=1}^m \eta_i = m$ and $\rank
  \obs = k$.
\end{proposition}
\begin{proof}
  Below, we use a slight abuse of notation and cast the entire
  optimization problem of $\tar$ to the first $m$ eigenvectors of
  $\fwd\ \prcov \fwd^*$. We treat $\eta$ as if it is $m-$dimensional,
  since by \ref{}, $\eta_i = 0, i > m$. This abuse of notation gives
  us the freedom to think of the problem at hand in $m-$dimensions. We
  will now find the optimal $\eta_i$'s.

@@

  Consequently:
  \begin{align} \label{eq:etas}
    \begin{split}
      \eta_i &= \frac{1}{2\alpha} - \sigma^2 \lambda_i^{-1}\\
      %
      %
      %
      &=\frac{m}{k} + \frac{\sigma^2}{k} \sum_{j=1}^k \lambda_j^{-1} - \sigma^2 \lambda_i^{-1}.%\\
      %
      %
      %
      %% &= \frac{m}{k} + \frac{\sigma^2}{k} \sum_{j \in A, j\neq i} \lambda_j^{-1} - \frac{k-1}{k}\sigma^2 \lambda_i^{-1}\\
      %% ,\ i \in A.
    \end{split}
  \end{align}
\end{proof}
An immediate corollary from Proposition \ref{prop:} and the formula
for posterior eigenvalues is:
\begin{corollary}
  If $\obs$ is optimal and $k := \rank \obs$, then:
  \begin{enumerate}
    \item The pushforwad/pullback (??) $\fwd \post$ covariance is
      $((\fwd \prcov \fwd^*)^{-1} + \sigma^{\pm 2} \obs^*\obs)$.
    \item The eigenvalues of said operator are
      \begin{equation}
        \eta_i = \begin{cases}
          \frac{m}{k} + \sigma^2 \frac{1}{k} \sum_{j=1}^k \lambda_j^{-1} & i \leq k \\
          \lambda_i^{-1} & i > k 
        \end{cases}.
      \end{equation}
  \end{enumerate}
\end{corollary}
%% Thus, for a given $A$, we know which $\eta_i$ are optimal.

>>>>

  Let $\obs$ an observation operator such that $\obs^*\obs$ has the
  same eigenvectors as $\fwd \prcov \fwd^*$. If $\eta_i > 0$ for
  $i\leq k$ and $\obs^*\obs$ has eigenvalues $\eta_i$, then $\obs$
  maximizes $\tar$ subject to $\sum_{i=1}^m \eta_i = m$ and to $\rank
  \obs = k$.
\end{proposition}
\begin{proof}
  Below, we use a slight abuse of notation and cast the entire
  optimization problem of $\tar$ to the first $m$ eigenvectors of
  $\fwd\ \prcov \fwd^*$. We treat $\eta$ as if it is $m-$dimensional,
  since by \ref{}, $\eta_i = 0, i > m$. This abuse of notation gives
  us the freedom to think of the problem at hand in $m-$dimensions. We
  will now find the optimal $\eta_i$'s.

@@

  Consequently:
  \begin{align} \label{eq:etas}
    \begin{split}
      \eta_i &= \frac{1}{2\alpha} - \sigma^2 \lambda_i^{-1}\\
      %
      %
      %
      &=\frac{m}{k} + \frac{\sigma^2}{k} \sum_{j=1}^k \lambda_j^{-1} - \sigma^2 \lambda_i^{-1}.%\\
      %
      %
      %
      %% &= \frac{m}{k} + \frac{\sigma^2}{k} \sum_{j \in A, j\neq i} \lambda_j^{-1} - \frac{k-1}{k}\sigma^2 \lambda_i^{-1}\\
      %% ,\ i \in A.
    \end{split}
  \end{align}
\end{proof}
An immediate corollary from Proposition \ref{prop:optimizer} and the formula
for posterior eigenvalues is:
\begin{corollary}
  If $\obs$ is optimal and $k := \rank \obs$, then:
  \begin{enumerate}
    \item The covariance of the pushforwad $\fwd_{*} \post$ is $((\fwd
      \prcov \fwd^*)^{-1} + \sigma^{-2} \obs^*\obs)^{-1}$.
    \item The eigenvalues of said operator are
      \begin{equation}
        \eta_i = \begin{cases}
          \frac{m}{k} + \sigma^2 \frac{1}{k} \sum_{j=1}^k \lambda_j^{-1} & i \leq k \\
          \lambda_i^{-1} & i > k 
        \end{cases}.
      \end{equation}
  \end{enumerate}
\end{corollary}
%% Thus, for a given $A$, we know which $\eta_i$ are optimal.
